plots with prolactin

### 2020-01-22 analysis/16_PRL.Rmd
new colors

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharnew) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)")
p1

@@

p2 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharnew) +
  labs(y = "PRL", x = "increasing time >>", subtitle = "Pituitary" ) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(axis.title.y  = element_text(face = "italic"))  +
  annotation_custom(control, ymin = 13.5, ymax = 15, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 8.5)   
p2

@@

p3 <- candidates.pit %>% 
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = BRCA1, fill = treatment, color = sex, alpha = sex)) +
    geom_boxplot() +
    theme_B3() +
      scale_alpha_manual(values = c(0.75,1)) +
  scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharnew) +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "BRCA1", subtitle = "Pituitary") +
  annotation_custom(control, ymin = 6.65, ymax = 7, xmin = -7.8) +
  annotation_custom(bldg, ymin = 6.65, ymax = 7, xmin = -5.8) +
  annotation_custom(lay, ymin = 6.65, ymax = 7, xmin = -3.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = -1.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 0.6) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 2.4) +
  annotation_custom(hatch, ymin = 6.65, ymax = 7, xmin = 4.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 6.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 8.4) +
  ylim(6.8,8.5) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  theme(axis.title.y  = element_text(face = "italic"))
p3

@@

p4 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharmaip) +
    labs(x = "increasing time >>", y = "PRL", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(13,22.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) +
    theme(axis.title.y  = element_text(face = "italic"))
p4

candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels3)

ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex), width=0.9) +
    scale_alpha_manual(values = c(0.75,1), guide=FALSE) +
    theme_B3() +
   theme(legend.position = "bottom", 
         legend.direction = "horizontal",
         legend.title = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.title.y = element_text(face = "italic")) + 
   scale_color_manual(values = sexcolors, guide=FALSE) +
  scale_fill_manual(values = colorscharmaip) +
    labs(x = "parental stage", y = "PRL", subtitle = "Pituitary") +
  ylim(c(14,22)) +
  theme()  +
  facet_wrap(~study2, scales = "free_x", shrink  = T) +
     guides(fill = guide_legend(nrow = 3, byrow = TRUE))

@@

```{r BRCA.pit.maip}
p5 <- ggplot(candidates.pit, aes(x = treatment, y = BRCA1)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(x = "increasing time >>", y = "BRCA1", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(6.8,8.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) +
    theme(axis.title.y  = element_text(face = "italic"))
p5

ggplot(candidates.pit, aes(x = PRL, y = BRCA1)) +
  geom_point(aes(alpha = sex,  color = 	treatment)) +
  geom_smooth(method = "loess", se=T, color = "darkgrey") +
  scale_color_manual(values = colorscharmaip2)  +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(subtitle = "Pituitary") +
  theme(axis.title  = element_text(face = "italic"),
        legend.title =  element_blank())

candidates.pit %>%
  filter(treatment %in% charlevels) %>%
ggplot( aes(x = PRL, y = BRCA1)) +
  geom_point(aes(alpha = sex,  color = 	treatment)) +
  geom_smooth(method = "loess", se=T, color = "darkgrey") +
  scale_color_manual(values = colorscharmaip2)  +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(subtitle = "Pituitary") +
  theme(axis.title  = element_text(face = "italic"),
        legend.title =  element_blank())

@@

## Genes an hormones (in progress, don't have all the bird ids lining up.)

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird
candidates.pit$X1 <- candidates.pit$V1

geneshormones <- left_join(candidates.pit, hormones) %>%
  select( -V1 ) %>%
  drop_na()

head(geneshormones$bird_id)
head(hormones$bird_id)

ggplot(geneshormones, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes(color = treatment)) +
  facet_wrap(~hormone, scales = "free_x") +
    geom_smooth(method = "lm", color = "grey")

prolactin2 <- read_csv("../results/07_prolactin2.csv")
head(prolactin2)
geneshormones2 <- left_join(candidates.pit, prolactin2) %>%
  drop_na()
head(geneshormones)

ggplot(geneshormones2, aes(x = plasma_conc, y = PRL)) +
  geom_point(aes( color = treatment)) +
  geom_smooth(method = "lm", color = "grey") +
  facet_wrap(~hormone, scales = "free") 
```

@@

p2 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = "none") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(y = "Pituitary PRL", x = "parental stage" ) +
  theme(axis.title.y  = element_text(face = "italic"),
        axis.text.x = element_blank())  +
  annotation_custom(control, ymin = 13.5, ymax = 15, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 8.5)

@@

@@

#WGCNAgenes <- read_csv("../results/08_PRL_associated.csv") %>% pull(x)
#WGCNAgenes <- c("FBXO5", "NUF2", "PTTG1", "BUB1", "PRL", "ASPM", "AURKA", "CDC20", "NEK2", "CKS2", 
#                  "MYC", "CCNB3", "FANCC", "STC1", "RACGAP1", "E2F7", "PLK1", "EXO1", "CENPI", "CDK1")
WGCNAgenes <- c("PRL", "PAX7", "ASPM", "AURKA",  "CDC20", "CENPF", "MYC",  "CDK1", "LBH", "BRCA1", "FOXM1", "FBXO5")

@@

p1 <- ggplot(WGCNAgenes.pit, aes(x = treatment, y = expression)) +
  geom_boxplot(aes(fill = treatment)) +
  facet_wrap(~genes, scales = "free_y") +
  theme_B3() +
  theme(legend.position = "none") +
  #scale_color_manual(values = sexcolors) +
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        strip.text = element_text(face = "italic")) +
  labs( x = "parental stage", y = "pituitary expression",
        subtitle = "Genes that are coexpressed with prolactin and regulate development")
i

>>>>

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharnew) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    #scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)")
p1

@@

p2 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharnew) +
  labs(y = "PRL", x = "increasing time >>", subtitle = "Pituitary" ) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(axis.title.y  = element_text(face = "italic"))  +
  annotation_custom(control, ymin = 13.5, ymax = 15, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 8.5)   
p2

@@

p3 <- candidates.pit %>% 
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = BRCA1, fill = treatment, color = sex)) +
    geom_boxplot() +
    theme_B3() +
      scale_alpha_manual(values = c(0.75,1)) +
  scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharnew) +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "BRCA1", subtitle = "Pituitary") +
  annotation_custom(control, ymin = 6.65, ymax = 7, xmin = -7.8) +
  annotation_custom(bldg, ymin = 6.65, ymax = 7, xmin = -5.8) +
  annotation_custom(lay, ymin = 6.65, ymax = 7, xmin = -3.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = -1.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 0.6) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 2.4) +
  annotation_custom(hatch, ymin = 6.65, ymax = 7, xmin = 4.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 6.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 8.4) +
  ylim(6.8,8.5) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  theme(axis.title.y  = element_text(face = "italic"))
p3

@@

p4 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal",
         axis.text.x = element_text(angle = 45, hjust = 1)) + 
   scale_color_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharmaip) +
    labs(x = "parental stage", y = "PRL", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(13,22.5)) +
    theme(axis.title.y  = element_text(face = "italic"))
p4

@@

```{r BRCA.pit.maip}
p5 <- ggplot(candidates.pit, aes(x = treatment, y = BRCA1)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(x = "parental stage", y = "BRCA1", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(6.8,8.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    theme(axis.title.y  = element_text(face = "italic"))
p5

plot_grid(p4 + theme(axis.title.x = element_blank(),
                     axis.text.x = element_blank()),
          p5 + labs(subtitle = NULL), nrow = 2, 
          rel_heights = c(0.45,0.55))

ggplot(candidates.pit, aes(x = PRL, y = BRCA1)) +
  geom_point(aes(alpha = sex,  color = 	treatment)) +
  geom_smooth(method = "loess", se=T, color = "darkgrey") +
  scale_color_manual(values = colorscharmaip2)  +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(subtitle = "Pituitary") +
   theme_B3() +
  theme(axis.title  = element_text(face = "italic"),
        legend.title =  element_blank())

candidates.pit %>%
  filter(treatment %in% charlevels) %>%
ggplot( aes(x = PRL, y = BRCA1)) +
  geom_point(aes(color = 	treatment)) +
  geom_smooth(method = "loess", se=T, color = "darkgrey") +
  scale_color_manual(values = colorscharmaip2)  +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(subtitle = "Pituitary") +
   theme_B3() +
  theme(axis.title  = element_text(face = "italic"),
        legend.title =  element_blank())

@@

@@

p2 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_fill_manual(values = colorscharmaip) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = "none") + 
  scale_color_manual(values = sexcolors) +
  labs(y = "Pituitary PRL", x = "parental stage" ) +
  theme(axis.title.y  = element_text(face = "italic"),
        axis.text.x = element_blank())  +
  annotation_custom(control, ymin = 13.5, ymax = 15, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 8.5)

@@

## genes

```{r}
geneinfo <- read_csv("../metadata/00_geneinfo.csv")
```

@@

#WGCNAgenes <- read_csv("../results/08_PRL_associated.csv") %>% pull(x)
#WGCNAgenes <- c("FBXO5", "NUF2", "PTTG1", "BUB1", "PRL", "ASPM", "AURKA", "CDC20", "NEK2", "CKS2", 
#              "MYC", "CCNB3", "FANCC", "STC1", "RACGAP1", "E2F7", "PLK1", "EXO1", "CENPI", "CDK1")

WGCNAgenes <- c("PRL", "PAX7", "ASPM", "AURKA",  "CDC20", "CENPF", "MYC",  
                "CDK1", "LBH", "BRCA1", "FOXM1", "FBXO5")

@@

p1 <- ggplot(WGCNAgenes.pit, aes(x = treatment, y = expression)) +
  geom_boxplot(aes(fill = treatment)) +
  facet_wrap(~genes, scales = "free_y") +
  theme_B3() +
  theme(legend.position = "none") +
  #scale_color_manual(values = sexcolors) +
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        strip.text = element_text(face = "italic")) +
  labs( x = "parental stage", y = "pituitary expression",
        subtitle = "Genes that are coexpressed with prolactin and regulate development") +
  scale_fill_manual(values = colorscharmaip)
p1 
```

## calisis candidates

```{r calisigenes, fig.height=6}

Calisigenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2"
                 )

calisisgenes.pit <- vsd.pit %>% dplyr::filter(genes %in% Calisigenes)
calisisgenes.pit <- as.data.frame(calisisgenes.pit)
row.names(calisisgenes.pit) <- calisisgenes.pit$genes
calisisgenes.pit <- pivot_longer(calisisgenes.pit, -genes, names_to = "V1", values_to = "expression")
head(calisisgenes.pit)
calisisgenes.pit <- left_join(colData.pit, calisisgenes.pit) %>%
  filter(study == "charcterization")
calisisgenes.pit$treatment <- factor(calisisgenes.pit$treatment, levels = alllevels)

calisisgenes.pit$genes <- factor(calisisgenes.pit$genes)
calisisgenes.pit$genesnum <- round(as.numeric(calisisgenes.pit$genes), digits = -1)

p2 <- ggplot(calisisgenes.pit, aes(x = treatment, y = expression)) +
  geom_boxplot(aes(fill = treatment)) +
  facet_wrap(~genes, scales = "free_y") +
  theme_B3() +
  theme(legend.position = "none") +
  #scale_color_manual(values = sexcolors) +
  theme( axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        strip.text = element_text(face = "italic")) +
  labs( x = "parental stage", y = "pituitary expression",
        subtitle = "Candidate genes")  +
  scale_fill_manual(values = colorscharmaip) 
p2
